Blowship - Untraceable Low-Latency Message Transfer via a Central Server

### 2014-03-17 paper.tex
fixed corrections

In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (P2P) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication. The primary reason behind a centeral server is to have a browser based service which needs a server to route for a pseudo-P2P network.

@@

Traditional cryptography hides the message being sent from one party to another. This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: the connection between sender and recipient.

@@

We present to the reader Untraceable Low-Latency Messaging via a Central Server. Our message system is accessed via the browser, allowing a person to browse to one central location and conveniently use this service, rather than using an external program for anonymity as with existing P2P services. The central server is acts as an intermediary and facilitator for the network of peers using it. The peers are used to obsfucate who is sending messages to whom, allowing the clients to maintain anonymity and message security, in as close to real time as possible.

@@

The anonymity mixes provide depends on many factors and was thoroughly analyzed by Serjantov in~\cite{trickle02}. In our system we use peers in the network as mixes, and will analyze their security using the known attacks that Serjantov presents (See Section~\ref{sec:PeersAsMixes} for a more in depth discussion).

@@

With a single server, PIR was discovered to still be possible, however. Computational PIR (first introduced by Chor \cite{CPIR}) uses computationally difficult mechanisms to prevent a server hosting a single database from learning which records users retrieve from it.

@@

Each successive party receives a message and an ID to forward that message to, and only that party can read its message. Importantly, any Penguin or Proletariat without collusion from Surge doesn't gain any information about the source or destination of the message it's passing along.

@@

This system is designed so that without collusion from Surge, Penguins or a Proletariat are powerless to do anything but to delay or fail to forward messages. They don't know the ID of the next person they are forwarding the message to (since it's encrypted with the server's key), and obtain no other information when forwarding messages. 
\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of the basic, na\"ive system described so far. 
Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $p_1 \ldots p_n$ where $p_i$ is a peer, Surge can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{p_1 \ldots p_n\}$ talked to Bob.
\item\textbf{Collusion.} If $s$ peers collude with Surge to form The Fort, then The Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $p_1 ... p_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases dramatically. 
\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB}$, the probability that Alice is talking to Bob, is $> 1/6$. If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ (if $n \subset s$), but the expectation is $E[P_{AB}] = 1/3$ which is very poor anonymity.

@@

MixMinion \cite{minion-design} solves these problems by having a small group of directory servers that only update nightly, having servers sign each other's directories, and ensuring that users download entire directories. These solutions are not feasible in our case since the set of online users is constantly in flux, and is likely to be too large to be sent to every user. Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.

In our system, however, a compromised Surge is disincentivized from lying about which peers are online. Consider a situation in which Alice wishes to send a message to Bob. If Surge doesn't report any non-colluding peers as online, then Alice won't send any messages to Bob since he appears to be offline. If Surge doesn't exclude non-colluding peers from the online list, however, Alice will inevitably include some of them in her chosen circuits. Since Surge doesn't know that Alice and Bob are communicating beforehand, he is forced to either include or exclude all non-colluding peers from the online-peers database as a whole.

@@

If Surge is willing to allow Bob to learn that he's lying about public keys, Surge can share a fake public key with the world and masquerade as Bob, intercepting all initial messages sent to him and potentially learning the identities of Bob's associates. Worse, he could masquerade only when he knows Bob is offline, while lying and saying that Bob is actually online.

>>>>

In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (P2P) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication. The primary reason behind a central server is to have a browser based service which needs a server to route for a pseudo-P2P network.

@@

Traditional cryptography hides the message being sent from one party to another. This is useful for many purposes, but there is an important aspect of your communication that is freely availble to anyone observing the transfer: the connection between sender and recipient.

@@

We present to the reader Untraceable Low-Latency Messaging via a Central Server. Our message system is accessed via the browser, allowing a person to browse to one central location and conveniently use this service, rather than using an external program for anonymity as with existing P2P services. The central server acts as an intermediary and facilitator for the network of peers using it. The peers are used to obsfucate who is sending messages to whom, allowing the clients to maintain anonymity and message security, in as close to real time as possible.

@@

The anonymity mixes provide depends on many factors and was thoroughly analyzed by Serjantov~\cite{trickle02}. In our system we use peers in the network as mixes, and will analyze their security using the known attacks that Serjantov presents (See Section~\ref{sec:PeersAsMixes} for a more in depth discussion).

@@

It was discovered that PIR is possible with a single server. Computational PIR (first introduced by Chor \cite{CPIR}) uses computationally difficult mechanisms to prevent a server hosting a single database from learning which records users retrieve from it.

@@

Each successive party receives a message and an ID to forward that message to, and only that party can read its message. Any Penguin or Proletariat without collusion from Surge doesn't gain any information about the source or destination of the message it's passing along.

@@

This system is designed so that without collusion from Surge, Penguins or a Proletariat are powerless to do anything but to delay or fail to forward messages. They don't know the ID of the next person they are forwarding the message to (since it's encrypted with the server's key), and obtain no other information when forwarding messages. 
\subsection{Security Flaws}
Here we will perform a simplified analysis of the security flaws of the basic, na\"ive system described so far. 
Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $p_1 \ldots p_n$ where $p_i$ is a peer, Surge can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{p_1 \ldots p_n\}$ talked to Bob.
\item\textbf{Collusion.} If $s$ peers collude with Surge to form The Fort, then The Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $p_1 ... p_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases dramatically. 
\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB}$, the probability that Alice is talking to Bob, is $> 1/6$. If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ (if $n \subset s$), but the expectation is $E[P_{AB}] = 1/3$ which is very poor anonymity.

@@

MixMinion \cite{minion-design} solves these problems by having a small group of directory servers that only update nightly, having servers sign each other's directories, and ensuring that users download entire directories. This solution is not feasible because set of online users is constantly changing. Sending the entire user list to every user each time someone logs on or off is infeasable. Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.

In our system, however, a compromised Surge is disincentivized from lying about which peers are online. Consider a situation in which Alice wishes to send a message to Bob. If Surge doesn't report any non-colluding peers as online, then Alice won't send any messages to Bob since he appears to be offline. If Surge doesn't exclude non-colluding peers from the online list, however, Alice will inevitably include some of them in her chosen circuits. Since Surge doesn't know that Alice and Bob are communicating beforehand, he is forced to either include or exclude all non-colluding peers from the online-peers database~as~a~whole.

@@

If Surge is willing to allow Bob to learn that he's lying about public keys, Surge can share a fake public key with the world and masquerade as Bob, intercepting all initial messages sent to him and potentially learning the identities of Bob's associates. Worse, he could masquerade as Bob when he knows Bob is offline.
